Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-11-08 manuscript/reviewer_reply.Rmd

Line 140: I’m curious why you didn’t consider spatial structure in the random effects here, using GMRF models or similar? One hand these models might be overkill if the habitat/environmental variables (which are spatially correlated) explain variability in richness, but the spatial correlation may pick up other sources of variability not accounted for by those variables.

Line 141-143: I think the paper thus far is pretty clear. I was hoping to see a few equations here – it helps me especially when components start to become hierarchical!

Line 163-164: again, I think equations could really help here to describe the baseline models. I think it’s also important to use these to clarify key details – for example, by training models on a site-by-site basis, you’re estimating separate parameters by site. For example with the uncorrelated noise model, you’re estimating unique variances by site right? Maybe say something like this, in addition to including equations.

"Line 180 – Maybe also mention this is in the forecast package – as you do with gbm below?"

--We have added this.

@@

Table 1 caption: without getting to more methods (below), I don’t understand the sentence ‘Environmental models were trained using all sites together, without information regarding which transects occurred at which site or during which year’.

Table 1: Just my personal preference, but I’d include the check marks and replace the ‘Xs’ with blank cells

Line 194-221: It seems for each approach you only considered the full models with all environmental covariates? I’m curious whether any of the covariates appeared to not improve explanatory power, and whether you considered models that dropped these uninformative predictors?

"Line 216: Cite randomForest / caret/ party R package – or whatever else you used?"

--We've cited this here.

### 2017-11-08 manuscript/draft.Rmd
cite randomforest directly where its used

**Time series models.** We used Auto-ARIMA models [based on the `auto.arima`
function in @forecast1] to represent an array of different time-series modeling
approaches. These models can include an autoregressive component (as in the
"naive" model, but with the possibility of longer-term dependencies in the
underlying process), a moving average component (where the noise can have serial
autocorrelation) and an integration/differencing component (so that the analysis
could be performed on sequential differences of the raw data, accommodating more
complex patterns including trends). The `auto.arima` function chooses whether to
include each of these components (and how many terms to include for each one)
using AICc [@forecast1]. Since there is no seasonal component to the BBS
time-series, we did not include a season component in these models. Otherwise we
used the default settings for this function [@forecast1].

@@

**Species Distribution Model: stacked random forests.** Species distribution
models (SDMs) predict individual species' occurrence probabilities using
environmental variables. Species-level models are used to predict richness by
summing the predicted probability of occupancy across all species at a site.
This avoids known problems with the use of thresholds for determining whether or
not a species will be present at a site [@calabrese2014; @pellissier2013].
Following @calabrese2014, we calculated the uncertainty in our richness estimate
by treating richness as a sum over independent Bernoulli random variables:
$\sigma^2_{richness} = \sum_i{p_i (1 - p_i)}$, where $i$ indexes species. By
itself, this approach is known to underestimate the true community-level
uncertainty because it ignores the uncertainty in the species-level probabilites
[@calabrese2014]. To mitigate this problem, we used an ensemble of 500 estimates
for each of the species-level probabilities instead of just one, propagating the
uncertainty forward. We obtained these estimates using random forests, a common
approach in the species distribution modeling literature. Random forests are
constructed by fitting hundreds of independent regression trees to
randomly-perturbed versions of the data [@cutler2007; @caruana2008]. When
correcting for observer effects, each of the 500 trees in our species-level
random forests used a different Monte Carlo estimate of the observer effects as
a predictor variable.

>>>>

**Time series models.** We used Auto-ARIMA models [based on the `auto.arima`
function in the package `forecast`; @forecast1] to represent an array of
different time-series modeling approaches. These models can include an
autoregressive component (as in the "naive" model, but with the possibility of
longer-term dependencies in the underlying process), a moving average component
(where the noise can have serial autocorrelation) and an
integration/differencing component (so that the analysis could be performed on
sequential differences of the raw data, accommodating more complex patterns
including trends). The `auto.arima` function chooses whether to include each of
these components (and how many terms to include for each one) using AICc
[@forecast1]. Since there is no seasonal component to the BBS time-series, we
did not include a season component in these models. Otherwise we used the
default settings for this function [@forecast1].

@@

**Species Distribution Model: stacked random forests.** Species distribution
models (SDMs) predict individual species' occurrence probabilities using
environmental variables. Species-level models are used to predict richness by
summing the predicted probability of occupancy across all species at a site.
This avoids known problems with the use of thresholds for determining whether or
not a species will be present at a site [@calabrese2014; @pellissier2013].
Following @calabrese2014, we calculated the uncertainty in our richness estimate
by treating richness as a sum over independent Bernoulli random variables:
$\sigma^2_{richness} = \sum_i{p_i (1 - p_i)}$, where $i$ indexes species. By
itself, this approach is known to underestimate the true community-level
uncertainty because it ignores the uncertainty in the species-level probabilites
[@calabrese2014]. To mitigate this problem, we used an ensemble of 500 estimates
for each of the species-level probabilities instead of just one, propagating the
uncertainty forward. We obtained these estimates using random forests
[@randomForest], a common approach in the species distribution modeling
literature. Random forests are constructed by fitting hundreds of independent
regression trees to randomly-perturbed versions of the data [@cutler2007;
@caruana2008]. When correcting for observer effects, each of the 500 trees in
our species-level random forests used a different Monte Carlo estimate of the
observer effects as a predictor variable.
